Racial and Ethnic Differences in ETI

### 2023-11-03 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
CF update

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/Documents/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("~/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```

>>>>

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Library/CloudStorage/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/Library/CloudStorage/Dropbox/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```
